# purrr basics {#intro}

```{r echo = FALSE}
library(purrr)
```

## map function 

### I want to... 

Start using {purrr}. 

### Here's how to:  

The base skeleton of {purrr} iteration functions are: 

```{r eval = FALSE}
library(purrr)
map(.x, .f, ...)
```

### Ok, but why? 

In this skeleton:

+ `.x` is a list, a data.frame or a vector.
+ `.f` is the function, formula or atomic vector that will be applied on each element of `.f`.

Here, what `map` does is applying the function to each element of a list. The returned object is always a list.

### See also 

+ [A introduction to purrr](https://github.com/cwickham/purrr-tutorial)

---

## map_* functions

### I want to... 

Control the output of my iterations. 

### Here's how to:

```{r}
# Returns a dbl
map_dbl(1:10, sqrt)
```

### Ok, but why?

You can control the output of your map with these functions: `map_lgl` `map_chr` `map_int` `map_dbl` `map_dfr` `map_dfc`. 

### See also 

+ [R for Data Science - 21.5 The map functions](http://r4ds.had.co.nz/iteration.html#the-map-functions)

---

## Mappers

### I want to... 

Create a function on the fly.

### Here's how to:

```{r}
map_dbl(1:10, ~ .x + 2)
```

### Ok, but why?

One sided formulaes, also called mappers, can be created as the `.f` argument of map. It is build with `~`, then `.x` refers to the element of the list in `.x`. 

When mapping on two elements, you can use `.x` and `.y`. With more than two elements, refer to them with `..1`, `..2`, `..3`, etc. 

### See also 

+ [R for Data Science - 21.5.1 Shortcuts](http://r4ds.had.co.nz/iteration.html#shortcuts)

---

## map on 2 elements

### I want to... 

map over two lists.

### Here's how to:

```{r}
map2_chr(letters, LETTERS, paste)
```

### Ok, but why?

`map2` and friends (`map2` `map2_lgl` `map2_int` `map2_dbl` `map2_chr` `map2_dfr` `map2_dfc`) allows to map over two elements. 

### See also 

+ [R for Data Science - 21.7 Mapping over multiple arguments](http://r4ds.had.co.nz/iteration.html#dealing-with-failure)

---

## map on more elements

### I want to... 

map over more than two lists. 

### Here's how to:

```{r}
l <- list(a = 1:3, b = 2:4, c = 3:5)
pmap_dbl(l, ~ ..1 + ..2 + ..3)
```

### Ok, but why?

`pmap` and friends (`pmap_lgl` `pmap_int` `pmap_dbl` `pmap_chr` `pmap_dfr` `pmap_dfc`) allows to map over more than two elements. 

### See also 

+ [R for Data Science - 21.7 Mapping over multiple arguments](http://r4ds.had.co.nz/iteration.html#mapping-over-multiple-arguments)

---

## Iteration for side effect

### I want to... 

Iterate only for side effect.

### Here's how to:

```{r}
walk(1:2, plot)
```

### Ok, but why?

`walk` is the silent conterpart of map, but invisible: you call it just for side effects. `map_*`, `map2_*`, `pwalk` and friends also exists. 

### See also

+ [R for Data Science - 21.8 Walk](http://r4ds.had.co.nz/iteration.html#walk)
