# Statistics {#stats}

```{r}
set.seed(2811)
```

## Compute the mean 

### I want to... 

Get the mean of vectors of unequal length. 

### Here's how to:

```{r}
numbers <- list(rnorm(10), rnorm(10), rnorm(1000))
trim <- 20
na_rm <- TRUE
pmap_dbl(list(numbers, trim, na_rm), ~ mean(..1, ..2,..3))
```

### Ok, but why?

`pmap` takes a list of list as an input, and send them to the function. In `.f`, you can refer to the list arguments with their position: here, `..1`, `..2` and `..3`.

### See also 

---

## Running a shapiro test

Given the dataset `airquality`.

### I want to... 

Look for normality on all columns, and know the one which are normal: 

### Here's how to:   

```{r}
map(airquality, shapiro.test) %>% keep(~ .x$p.value > 0.05)
```

### Ok, but why? 

In R, data.frame are __lists of vectors of same length__. So, you can apply a function the same way you would apply a function on any list. Here, we are mapping a `shapiro.test`, on all columns, and we `keep` only the elements with a `.x$p.value` which is more than 0.05.

### See also 

+ [A Crazy Little Thing Called {purrr} - Part 6 : doing statistics](http://colinfay.me/purrr-statistics/)

---

## Test only numeric columns

### I want to... 

Make sure I make my statistical test on numeric values. 

### Here's how to:   

```{r}
map_if(.x = iris, .p = is.numeric, .f = shapiro.test)
```

### Ok, but why? 

`map_if` runs `.f` only if the `.x` verifies the condition `.p`.

### See also 

+ [A Crazy Little Thing Called {purrr} - Part 6 : doing statistics](http://colinfay.me/purrr-statistics/)

---

## cor.test

### I want to... 

Make a bulk cor.test of all my variables.

### Here's how to:   

```{r}
library(tidystringdist) # Works since v0.1.2 
comb <- tidy_comb_all(names(airquality))
pmap(comb, ~ cor.test(airquality[[.x]], airquality[[.y]])) %>% 
  map_df(broom::tidy) %>% 
  cbind(comb, .) %>%
  select(V1:parameter)
```

### Ok, but why? 

`comb` is a table containing all combinations of the names of the columns. What we do is mapping a `cor.test` on all these combinations by extracting, each time, the column as a vector, with `airquality[[.x]]` and `airquality[[.y]]`. 

`pmap` allows to use a list as a signe input.

### See also 

+ [A Crazy Little Thing Called {purrr} - Part 6 : doing statistics](http://colinfay.me/purrr-statistics/)

---

## Linear regression

### I want to... 

Get the r.squared of each of the possible lm of airquality combinations.

### Here's how to:   

```{r}
res <- pmap(comb, ~ lm(airquality[[.x]] ~ airquality[[.y]]))
get_rsquared <- compose(as_mapper(~ .x$r.squared), summary)
map_dbl(res, get_rsquared)
```

### Ok, but why? 

We're building a model of all combinations with `pmap`, just as before with `cor.test`.

Then, the `get_rsquared` function is a composition of extracting the r.squared of the summary of a lm result. `compose(x, y)` allows to build `x(y())`. Here, we are combining a mapper extracting the `r.squared` element out of the `summary()` of a `lm`.

### See also 

+ [A Crazy Little Thing Called {purrr} - Part 6 : doing statistics](http://colinfay.me/purrr-statistics/)

---

## significant r.squared

### I want to... 

Know if some r.square are above O.5 :

### Here's how to:   

```{r}
res <- pmap(comb, ~ lm(airquality[[.x]] ~ airquality[[.y]]))
get_rsquared <- compose(as_mapper(~ .x$r.squared), summary)
map_dbl(res, get_rsquared) %>% some(~ .x > 0.5)
```

### Ok, but why? 

`some` checks if any of the input validate the condition.

### See also 

+ [A Crazy Little Thing Called {purrr} - Part 6 : doing statistics](http://colinfay.me/purrr-statistics/)

---

## test and validation

### I want to... 

Create 20 test and validation datasets.

### Here's how to:   

```{r message=FALSE}
# From http://biostat.mc.vanderbilt.edu/wiki/pub/Main/DataSets/titanic3.csv
titanic <- readr::read_csv("titanic.csv")
train <- rerun(20, sample_frac(titanic, size = 0.8))
validation <- map(train, ~ anti_join(titanic, .x))
```

### Ok, but why? 

`rerun` runs the sampling  20 times. To obtain the 20 validation sets, we anti-join each elements of the train list with the original dataframe. That way, `train[1]` + `validation[1]` = `titanic`, `train[2]` + `validation[2]` = `titanic`, etc

### See also 

+ [A Crazy Little Thing Called {purrr} - Part 6 : doing statistics](http://colinfay.me/purrr-statistics/)

---

## rpart

### I want to... 

Create 20 `rpart`, modeled on my 20 elements in the `test` list.

### Here's how to:   

```{r}
library(rpart)
rpart_pimped <- partial(rpart, formula = survived ~ sex, method = "class")
res <- map(train, rpart_pimped)
res[[1]]
```

### Ok, but why? 

`partial` allows to build a prefil function, which is then mapped on each element.

### See also 

+ [A Crazy Little Thing Called {purrr} - Part 6 : doing statistics](http://colinfay.me/purrr-statistics/)

---

## Make prediction

### I want to... 

Make prediction based on my models

### Here's how to:   

```{r}
prediction <- map2(validation, res, ~ predict(.y, .x, type = "class"))
w_prediction <- map2(validation, prediction, ~ mutate(.x, prediction = .y))
```

### Ok, but why? 

`map2` allows to map on two arguments.

### See also 

+ [A Crazy Little Thing Called {purrr} - Part 6 : doing statistics](http://colinfay.me/purrr-statistics/)

---

## Confusion matrix

### I want to... 

Create a conf matrix on all these results:

### Here's how to:   

```{r}
library(caret)
conf_mats <- map(w_prediction, ~ confusionMatrix(.x$prediction, .x$survived))
```

### Ok, but why? 

You can use `.x` as many times as you want in `.f`.

### See also 

+ [A Crazy Little Thing Called {purrr} - Part 6 : doing statistics](http://colinfay.me/purrr-statistics/)

---

## Sensitivity and Specificity

### I want to... 

Detect which models have a specificity above 0.7 and sensitivity above 0.85 (randomly chosen numbers).

### Here's how to:   

```{r}
keep_index <- function(.x, .p, ...) {
  sel <- purrr:::probe(.x, .p, ...)
  which(sel)
}
sens <- map_dbl(conf_mats, ~ .x$byClass["Sensitivity"]) %>% keep_index(~ .x > 0.85)
spec <- map_dbl(conf_mats, ~ .x$byClass["Specificity"]) %>% keep_index(~ .x > 0.7)
keep(sens, map_lgl(sens, ~ .x %in% spec))
```

### Ok, but why? 

We have created a function that returns the position of elements that validates a condition. `sens` is the vector containing the position with sensitivity above 0.85, `spec` the vector for specificity above 0.7.

Then, we pass to `keep` a vector of logical built with `map_lgl`. This vector tells if each elements of `sens` is or isn't in `spec`.

### See also 

+ [A Crazy Little Thing Called {purrr} - Part 6 : doing statistics](http://colinfay.me/purrr-statistics/)
