# Text Mining {#tm}

## Build regex 

### I want to...

Automatically build a regex with or `|`

### Here's how to: 

```{r}
regex_build <- function(...){
    reduce(list(...), ~ paste(.x, .y, sep = "|"))
}
regex_build("one","two","three", "four")
```

### Ok, but why?

`reduce` turns a list into one value by recursively applying a binary function to the list. In other words, `reduce(list("one","two","three"), ~ paste(.x, .y, sep = "|"))` does `paste("one", paste("two", paste("three", "four", sep = "|"), sep = "|"), sep = "|")`. 

### See also

---

## Regex extraction 

### I want to... 

Extract the elements from a list of words that match a regex

### Here's how to: 

```{r}
# Random words from https://www.randomlists.com/random-words
words <- c("copper", "explain", "ill-fated", "truck", "neat","unite","branch","educated","tenuous", "hum","decisive","notice")
# Extract words that end with a "e"
my_regex <- "e$"
keep(words, ~ grepl(my_regex, .x))
```

### Ok, but why? 

`keep` only keeps the element matching the predicate. Here, we're using `grepl`, that returns TRUE or FALSE if the expression is found in the string. 

### See also

---

## Collapse a list of words

Given the following list of hashtags: 

```{r}
hash <- list(tweet1 = c("#RStats", "#Datascience"), tweet2 = c("#RStats", "#BigData"))
```

### I want to... 

Turn my list of words into a simple vector.

### Here's how to: 

```{r}
simplify(hash) %>% paste(collapse = " ")
```

### Ok, but why? 

Simplify turns a list of n\*m elements into a vector of lenght n\*m. We then paste all the elements together, using the `collapse` argument from `paste`.

### See also


